Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 paper.tex
Improve text and respond to reviewer wrt success rate.

\caption{Random goal configurations solving a reaching task. All the
  configurations are balanced and collision-free, and the right hand of the character
  reaches the orange ball. Note that the ball is also an obstacle.}
\label{fig:goal}
\end{figure}

@@

We present in Fig.~\ref{fig:wb-shelves} an illustration of 
the use of randomized motion planning 
on complex manipulation problems. The humanoid robot HRP-2 faces shelves. It has to: (i) grasp
a ball lying on a shelf, (ii) put it on a higher shelf, (iii) come back to a natural
rest configuration. The statical balance manifold on which the planning takes place is
defined by tasks constraining the robot feet and CoM. The goal of the first problem

FIXME: what follows is not clear, rephrase to say that the hand
position is fixed and that it can rotate along the vertial axis.

is defined by a hand configuration task (3 positions and 2 orientations), and a gaze task
(the robot has to look at the ball). The goal of the second problem is defined by a 
different hand configuration and the gaze task.
Finally, the goal of the third problem is the rest configuration.

For the two reaching motions, we generate 8 random goal configurations (Section~\ref{sec:goal-sampling}).

Extension 1 presents a video of this motion after an optimization step.

@@

We have run this set of motion planning problems 20 times. The results are compiled in Table~\ref{table:reaching}.
\begin{table}
\begin{tabular}{l|r|r|r|r|}
\cline{2-5}
& min & max & average & average \\ 
&&&& per problem \\
\hline
\multicolumn{1}{|l|}{number of nodes} & 43.00 & 481.00 & 102.70 \\
\cline{1-4}
\multicolumn{1}{|l|}{goal generation time (s)} & 1.00 & 1.56 & 1.22\\
\hline
\multicolumn{1}{|l|}{planning time (s)} & 67.36 & 376.84 & 134.28 & 44.76\\
\hline
\end{tabular}
\caption {\textbf{Experimental results on 20 runs: Each run consists
    of 3 motion planning problems and 2 goal generations for the three
    phases. Time is expressed in seconds.}}
\label{table:reaching}
\end{table}

Among all calls to \texttt{constraint-solver}, the average number of iterations is 6.5 and the success rate is above 95 percent.

>>>>

\caption{Random goal configurations solving a reaching task. All the
  configurations are balanced and collision-free, and the right hand of the character
  reaches the orange ball.}
\label{fig:goal}
\end{figure}

@@

\textbf{We present in Fig.~\ref{fig:wb-shelves} an illustration of the
  use of randomized motion planning on complex manipulation
  problems. The humanoid robot HRP-2 faces shelves. It has to: (i)
  grasp a ball lying on a shelf, (ii) put it on a higher shelf, (iii)
  come back to a natural rest configuration. We can hence define three
  separate constrained motion planning problems where the planning
  manifold $\manifold$ is the static balance manifold defined in
  \ref{sec:wb}; the goal manifold of problem (i) is defined by a hand
  pose constraint (the hand must be horizontal and its position has to
  coincide with the ball initial position), and a gaze constraint (the
  robot has to look at the ball in its initial position). Similarly,
  the goal manifold of problem (ii) is defined by hand and gaze
  constraints that correspond to the position of the ball on the
  higher shelf. Finally, we define the rest configuration as the
  single goal configuration for problem (iii).}

\textbf{Note that for phases (i) and (iii) the ball is also considered
  as an obstacle. This is necessary to prevent the robot grasping hand
  from colliding with the ball during the approach (respectively
  retraction) phase.}

\textbf{For the two reaching motions in (i) and (ii), we first
  generate 8 random goal configurations
  (Section~\ref{sec:goal-sampling}), then we solve the three
  constrained motion planning problems separately. As randomized
  motion planning algorithms produce, a classic shortcut method is
  used to optimize and shorten the paths. Extension 1 presents a
  video of the concatenated motion.}

\textbf{We have run this set of motion planning problems 20 times;
  results are compiled in Table~\ref{table:reaching}. We have also
  measured the performance of \texttt{constraint-solver} (Algorithm
  \ref{algo:newton}) when used to project configurations on
  $\manifold$; the average number of iterations is 6.5 per call, and
  the success rate, i.e. the ratio of the number of successfully
  projected configurations over the total number of calls, is above 95
  percent.}

@@

\begin{table}
\begin{tabular}{l|r|r|r|r|}
\cline{2-5}
& min & max & average & average \\ 
&&&& per problem \\
\hline
\multicolumn{1}{|l|}{number of nodes} & 43.00 & 481.00 & 102.70 \\
\cline{1-4}
\multicolumn{1}{|l|}{goal generation time (s)} & 1.00 & 1.56 & 1.22\\
\hline
\multicolumn{1}{|l|}{planning time (s)} & 67.36 & 376.84 & 134.28 & 44.76\\
\hline
\end{tabular}
\caption {\textbf{Experimental results on 20 runs: Each run consists
    of 3 motion planning problems and 2 goal generations for the three
    phases. Time is expressed in seconds.}}
\label{table:reaching}
\end{table}
